---
title: "Exercise 1"
format: html
editor: visual
---

## Exercise 1

### Generating 100 Values

In the first Step, we generate 100 values with log-normal distribution mu=5 and sigma = 0.5

```{r}
values <- rlnorm(100, meanlog = 5, sdlog = 0.5)
```

### Import ggplot2 library

```{r}
library(ggplot2)
```

### Linear Histogram

After importing the library, we can use the command geom_histogram to create a histogram.

```{r}

ggplot(data = data.frame(values), aes(x = values)) +
  geom_histogram() +
  labs(title = "Histogram", x = "Values linear scale", y = "Frequency")

```

### Log Histogram

To create the log scale we can add the command scale_x_log10

```{r}
ggplot(data = data.frame(values), aes(x = values)) +
  geom_histogram() + 
  labs(title = "Histogram", x = "Values log scale", y = "Frequency") +
  scale_x_log10()
```

### Violin Plot

geom_violin creates a violin plot.

```{r}
ggplot(data = data.frame(values), aes(x = " ", y = values)) +
  geom_violin() +
  labs(title = "Violin Plot", y = "Values")
```

### Mean Value and Standard Deviation

Mean of the sampled values:

```{r}
mean(values)
```

Standard deviation of the sampled values:\`

```{r}
sd(values)
```
